Gamification can Change the Traditonal Educational System

### 2024-04-19 paper/paper.qmd
added the data cleaning section

>>>>

The R package used for cleaning data were In this paper, the analysis is carried out using the statistical programming language `R` [@citeR], with the help of extra packages including `arrow` [@arrow], `kableExtra` [@kableExtra], `gridExtra`[@gridExtra], `knitr` [@knitr],   `modelsummary`[@modelsummary], `tidyverse` [@Tidyverse].
